---
title: "Homework 6"
author: "Linh Tran"
date: "11/29/2020"
output: github_document
---

```{r setup, include = FALSE}

library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d


set.seed(1)
```


# Problem 1

Load dataset

```{r}
homicide_df =
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>%    #most of coefficient estimates are negative, meaning resolution becomes less likely in comparison to reference group. 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities

```{r error = TRUE}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial)),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))

```


Make a plot comparing OR between male and female homicide victim along with CI

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


# Problem 2

Load and clean the data 

```{r}
baby_df = 
  read_csv("data/birthweight.csv") %>%
  mutate(
    babysex = as.factor(recode(babysex, `1` = "male", `2` = "female")),
    frace = as.factor(recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown")),
    mrace = as.factor(recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other")),
    malform = as.factor(recode(malform, `0` = "absent", `1` = "present"))
    )

```

**Modeling process** 

Proposed model

```{r}
summary(lm(bwt ~ ., data = baby_df))  #babysex, bhead, blength, delwt, gaweeks, parity (*), smoken.


proposed_model = lm(bwt ~ gaweeks + smoken, data = baby_df)
summary(proposed_model)
```

**A plot of model residuals against fitted values**

```{r}
baby_df %>% 
  modelr::add_residuals(proposed_model) %>% 
  ggplot(aes(x = resid)) +
  geom_density()

baby_df %>% 
  modelr::add_residuals(proposed_model) %>% 
  ggplot(aes(x = gaweeks, y = resid)) +
  geom_point() 
```

Two other models for comparison:

```{r}
model1 = lm(bwt ~ blength + gaweeks, data = baby_df)
summary(model1)

model2 = lm(bwt ~ bhead * blength * babysex, data = baby_df)
summary(model2)

```

**Cross-validated predicted error**

```{r}
cv_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    model1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model2  = map(train, ~lm(bwt ~ bhead + blength + babysex, data = .x)),
    proposed_model  = map(train, ~lm(bwt ~ gaweeks + smoken, data = .x))
    ) %>% 
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_proposed_model = map2_dbl(proposed_model, test, ~rmse(model = .x, data = .y))
    )
```

The distribution of RMSE values for each model.

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


# Problem 3

Download dataset and just focus on Central Park, NY data. 

```{r}

```



use bootstraps to obtain distribution for parameters interested in. 
Fit a linear model of tmax and tmin. Proporiton of r squared value (broom::glance) and log of (bo + b1) (broom::tidy)
